Tail Indices and Scale Parameters in Financial Time Series

### 2017-03-22 papers/FX/draft.tex
Rearranged the sections.

\begin{proof}
  Let
  \begin{equation}
    \label{eq:xxie2}
    \hat \phi := \argmax_{0 < \phi \leq 1} \mathcal U(F, \phi)
  \end{equation}
  We have
  \[
  G(F) = \mathcal U(F, \hat\phi)
  \]
  It follows
  \begin{eqnarray}
    \pd{G(F)}{\alpha}
    &=&
    \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, K, \hat\phi)
    + \pd{\mathcal U(F, \phi)}{\phi}(\alpha, K, \hat\phi)
    \pd{\hat\phi}{\alpha}(\alpha, K)
    \label{eq:xxie3}
  \end{eqnarray}
  The definition \eqref{eq:xxie2} implies $\forall \alpha > 1$
  \begin{equation}
    \label{eq:xxie4}
    \pd{\mathcal U(F, \phi)}{\phi}(\alpha, K, \hat \phi) = 0
  \end{equation}
  So the second term of \eqref{eq:xxie3} vanishes. It remains to show
  \begin{eqnarray*}
    \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, K, \hat \phi)
    &>& 0
  \end{eqnarray*}
  From \eqref{eq:xxie1.0}, it follows
  \begin{eqnarray*}
    \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, K, \hat\phi)
    = \opd{\alpha}\E[u((1 - \hat\phi) e^r + \hat\phi e^X) \1{X < 0}]
  \end{eqnarray*}
  The function $u((1 - \hat\phi) e^r + \hat\phi e^X)$ is obviously increasing
  with $X$. It follows
  \begin{eqnarray*}
    && \pd{f(x; \alpha, K)}{\alpha} \\
    &=& \opd{\alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} \\
    &=&
    - {K^\alpha \over (K - x)^{\alpha + 1}}
    \left[
      \alpha
      \ln\left(
        1 - {x \over K}
      \right) - 1
    \right]
  \end{eqnarray*}
  It is easily checked that when $x < K(1 - e^{1/\alpha}) < 0$,
  \[
  \opd{\alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} < 0
  \]
  and when $K(1 - e^{1/\alpha}) < x < 0$,
  \[
  \opd{\alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} > 0
  \]
  This is the second case of lemma \ref{lemma:I}. So we have
  \begin{eqnarray*}
    \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, K, \hat\phi) &>& 0
  \end{eqnarray*}
  As for $\pd{G(F)}{K}$, by the same argument as for
  $\pd{G(F)}{\alpha}$, it suffices to show
  \[
  \pd{\mathcal U(F, \phi)}{K}(\alpha, K, \hat\phi) < 0
  \]
  We have
  \[
  \pd{\mathcal U(F, \phi)}{K}(\alpha, K, \hat\phi)
  = \opd{K} \E \left[
    u((1 - \hat\phi) e^r + \hat\phi e^X) \1{X < 0}
  \right] 
  \]
  and
  \begin{eqnarray*}
    && \pd{f(x; \alpha, K)}{K} \\
    &=& \opd{K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} \\
    &=&
    -\alpha K^{\alpha - 1} {
      \alpha x + K
      \over
      (K - x)^{\alpha + 2}
    }
  \end{eqnarray*}
  Clearly, when $x < -\alpha/K$
  \[
  \opd{K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} > 0
  \]
  and when $-\alpha/K < x < 0$
  \[
  \opd{K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} < 0
  \]
  So by the 1st case of remark \ref{remark:I} we conclude
  \[
  \pd{\mathcal U(F, \phi)}{K}(\alpha, K, \hat\phi) < 0  
  \]
\end{proof}
By numerically integration and optimization with respect to $\phi$,
the value of $\hat\phi$ can be obtained for given $u(\cdot)$ and given
values of $K, K', \alpha, \beta$. Figures \ref{fig:phi_hat_pareto5e-1}
and \ref{fig:phi_hat_pareto4} show the values of $\hat\phi$ for
$u(C) = -\frac{C^{-\xi}}{\xi}$ with $\xi = 1/2, 4$ respectively.
$\beta=\alpha$ and $K'=K$ in both figures.
\begin{figure}
  \begin{subfigure}[b]{0.5\linewidth}
    \includegraphics[width=\textwidth]{phi_hat_pareto5e-1.pdf}
    \caption{$\hat\phi$}
    \label{fig:phi_hat_pareto5e-1}
  \end{subfigure}
  \begin{subfigure}[b]{0.5\linewidth}
    \includegraphics[width=\textwidth]{phi_hat_pareto4.pdf}
    \caption{$\hat\phi$}
    \label{fig:phi_hat_pareto4}
  \end{subfigure}
  \caption{$\hat\phi$, the optimal equity allocation when the utility
    function is $u(C) = -{C^{-\xi} \over \xi}$ for $\xi = 1/2, 4$.
  }
\end{figure}

@@

\subsection{Student's t-distributed equity return}
It is a common practice to use Student's t-distribution to model the
stationary distribution of equity returns. So it is of interest to
find out what implications this distribution has when it is combined
with the PDA preference. Formally we assume
\[
f(x; \nu) = c(\nu) \left(
  1 + {x^2 \over \nu}
\right)^{-(\nu + 1)/2}
\]
where $\nu > 1$ and
\[
c(\nu) = {
  \Gamma({\nu + 1 \over 2})
  \over
  \Gamma(\nu/2) \sqrt{\nu \pi}
}
\]
\begin{lemma}
  \label{lemma:II}
  There exists $x_0 > 0$ such that $\pd{f}{\nu}(x_0, \nu) = 0$ and
  $\forall x \in (0, x_0), \pd{f}{\nu}(x, \nu) > 0$ and
  $\forall x \in (x_0, \infty), \pd{f}{\nu}(x, \nu) < 0$.
\end{lemma}

We consider the case where the utility function is simply
$u(\cdot) = \ln(\cdot)$. This corresponds to the limiting case of
\eqref{eq:power_utility} as $\gamma \to 0$. Straightforward
computation gives
\begin{eqnarray*}
  && \mathcal U(F, \phi) \\
  &=&
  \int_{0}^{\infty}
  \left[
    \ln(C(x)) + (1 + b)\ln(C(-x))
  \right]
  f(x, \nu) dx
  + b \int_{0}^{q}
  \ln(C(x))
  f(x, \nu) dx \\
  &&
  - b \ln(C(q)) F(q, \nu)
\end{eqnarray*}
where $C(\cdot)$ is defined in \eqref{eq:xxie1}. Notice that
when $b = 0$, $\mathcal U(F, \phi)$  reduces to $\E u(C(X))$.
Also observe $\ln(C(x)C(-x))$ is an increasing function:
\begin{eqnarray*}
  \pd{C(x) C(-x)}{x}
  &=&
  \phi e^r (1 - \phi) (e^x - e^{-x}) > 0
\end{eqnarray*}
Thus by 1st case of remark \ref{remark:I} and lemma \ref{lemma:II},
$\pd{\mathcal U(F, \phi))}{\nu} < 0$ for all $\phi$. Hence all
investors guided by this utility function would be seeking the
smallest $\nu$, i.e. the heaviest tail in the market.

@@

@@

\section{Hill Estimator}
\label{sec:Hill}
There have been several estimators for the tail index proposed in the
literature, e.g. Hill (1975) \cite{hill1975simple}, Pikands (1975)
\cite{pickands1975statistical}, Dekkers and Einmahl and De Haan (1989)
\cite{dekkers1989moment}. See also Embrechts and Kl\"uppelberg and
Mikosch (1997)\cite{Embrechts1997}. The most popular of these is
arguably Hill (1975) \cite{hill1975simple}:
\[
\hat \alpha = \left[
  {1 \over k} \sum_{i=1}^k \ln {x_{(i)} \over x_{(k+1)}}
  \right]^{-1}
\]
where $x_{(i)}$ is the $i$-th upper order statistic of a sample
$x_1, x_2, ..., x_n$. It has been shown that the Hill estimator is
applicable to 
\begin{itemize}
\item iid random variables (Mason (1982) \cite{mason1982laws})
\item a weakly dependent sequence (Rootz{\'e}n, Leadbetter,
  and de Haan \cite{rootzen1992tail})
\item a linear process (Resnick and St{\u{a}}ric{\u{a}} (1995)
  \cite{resnick1995consistency}).
\end{itemize}
In these cases it is shown that, if $k \to \infty$ and $k/n \to 0$
as $n \to \infty$, the Hill estimator is weakly consistent, i.e.
\[
\sqrt k (\hat \alpha - \alpha) \overset{d}{\to} N(0, \alpha^2)
\]

%% \subsubsection{The Energy and the Consumer Staples sectors of S\&P 500}
Figure \ref{fig:Energy_lower},
\ref{fig:Consumer_Staples_lower},
and \ref{fig:Information_Technology_lower}
show the Hill estimates of the
lower tail indices of the ``energy'', ``consumer staples'' and ``information
technology'' sectors of the S\&P 500 index, respectively.
\begin{figure}[htb!]
  \centering
  \includegraphics[width=\textwidth]{Energy_lower.pdf}
  \caption{Hill estimates of the lower tail indices of 32 stocks'
    daily return series in the {\it Energy} sector of Standard \& Poor
    500 index. Each circle coresponds to a Hill estimate; the grey
    triangles above and below it mark the 97.5\% and 2.5\% quantiles
    of its approximate normal distribution.
    The low and high red lines mark the median of the 2.5\% quantiles
    and median of the 97.5\% quantiles, respectively.
    The data are from {\it Yahoo Finance} and the labels on
    the horizontal axis are Yahoo symbols of the stocks. The data span
    from 2010-01-01 to 2015-01-01 and comprise $n=1304$
    observations. $k=(\ln n)^2 = 49$ lower order statistics are used
    for computing $\alpha_n$. 
  }
  \label{fig:Energy_lower}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[width=\textwidth]{Consumer_Staples_lower.pdf}
  \caption{Hill estimates of the lower tail indices of 30 stocks'
    daily return series in the {\it Consumer Staples} sector of
    Standard \& Poor 500 index.
  }
  \label{fig:Consumer_Staples_lower}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[width=\textwidth]{Information_Technology_lower.pdf}
  \caption{Hill estimates of the lower-tail indices of 42 stocks' daily
    return series in the {\it Information Technology} sector of S\&P
    500 index.
  }
  \label{fig:Information_Technology_lower}
\end{figure}

\section{Hybrid estimation of the assumed distribution function}
\label{sec:hybrid_estimation}
We adopt a hybrid procedure to estimate the parameters of the
distribution function assumed in \eqref{eq:X_distr}: First we
obtain a Hill estimate of the lower-tail indices of an
equity return and fix $\alpha$ in \eqref{eq:X_distr}
to its Hill estimate. Then we estimate $K$ by maximizing
the likelihood function with fixed $\alpha$. Obviously we take only
negative observations and hence condition on $X < 0$.

@@

\section{Pickand's Estimator}
Pickands (1975) \cite{pickands1975statistical} proposed a different
approach to estimate the tail index than that of Hill. Assume
$\{x_i\}_{i=1}^n$ are samples from the distribution of $X$ and let $U(t)$
denote the quantile of $1 - 1/t$ of this distribution, i.e.
\[
P(X > U(t)) = {1 \over t}
\]
The key idea of Pickands' estimator is to observe
\[
\lim_{t \to \infty} {
  U(c(t) t) - U(t)
  \over
  U(t) - U(t/c(t))
} = 2^{1/\alpha}
\]
for any function $c(t)$ satisfying $c(t) \to 2$ as $t \to \infty$.
Pickands formulated the estimation problem in terms of the extreme
value index $\xi$, which is the reciprocal of the tail index $\alpha$
when the distribution of $X$ is regularly varying (cf. Embrechtsm,
Kl\"uppelberg and Mikosch \cite{Embrechts1997}).

>>>>

\begin{proof}
  Let
  \begin{equation}
    \label{eq:xxie2}
    \hat \phi := \argmax_{0 < \phi \leq 1} \mathcal U(F, \phi)
  \end{equation}
  We have
  \[
  G(F) = \mathcal U(F, \hat\phi)
  \]
  It follows
  \begin{eqnarray}
    \pd{G(F)}{\alpha}
    &=&
    \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, K, \hat\phi)
    + \pd{\mathcal U(F, \phi)}{\phi}(\alpha, K, \hat\phi)
    \pd{\hat\phi}{\alpha}(\alpha, K)
    \label{eq:xxie3}
  \end{eqnarray}
  The definition \eqref{eq:xxie2} implies $\forall \alpha > 1$
  \begin{equation}
    \label{eq:xxie4}
    \pd{\mathcal U(F, \phi)}{\phi}(\alpha, K, \hat \phi) = 0
  \end{equation}
  So the second term of \eqref{eq:xxie3} vanishes. It remains to show
  \begin{eqnarray*}
    \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, K, \hat \phi)
    &>& 0
  \end{eqnarray*}
  From \eqref{eq:xxie1.0}, it follows
  \begin{eqnarray*}
    \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, K, \hat\phi)
    = \opd{\alpha}\E[u((1 - \hat\phi) e^r + \hat\phi e^X) \1{X < 0}]
  \end{eqnarray*}
  The function $u((1 - \hat\phi) e^r + \hat\phi e^X)$ is obviously increasing
  with $X$. It follows
  \begin{eqnarray*}
    && \pd{f(x; \alpha, K)}{\alpha} \\
    &=& \opd{\alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} \\
    &=&
    - {K^\alpha \over (K - x)^{\alpha + 1}}
    \left[
      \alpha
      \ln\left(
        1 - {x \over K}
      \right) - 1
    \right]
  \end{eqnarray*}
  It is easily checked that when $x < K(1 - e^{1/\alpha}) < 0$,
  \[
  \opd{\alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} < 0
  \]
  and when $K(1 - e^{1/\alpha}) < x < 0$,
  \[
  \opd{\alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} > 0
  \]
  This is the second case of lemma \ref{lemma:I}. So we have
  \begin{eqnarray*}
    \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, K, \hat\phi) &>& 0
  \end{eqnarray*}
  As for $\pd{G(F)}{K}$, by the same argument as for
  $\pd{G(F)}{\alpha}$, it suffices to show
  \[
  \pd{\mathcal U(F, \phi)}{K}(\alpha, K, \hat\phi) < 0
  \]
  We have
  \[
  \pd{\mathcal U(F, \phi)}{K}(\alpha, K, \hat\phi)
  = \opd{K} \E \left[
    u((1 - \hat\phi) e^r + \hat\phi e^X) \1{X < 0}
  \right] 
  \]
  and
  \begin{eqnarray*}
    && \pd{f(x; \alpha, K)}{K} \\
    &=& \opd{K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} \\
    &=&
    -\alpha K^{\alpha - 1} {
      \alpha x + K
      \over
      (K - x)^{\alpha + 2}
    }
  \end{eqnarray*}
  Clearly, when $x < -\alpha/K$
  \[
  \opd{K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} > 0
  \]
  and when $-\alpha/K < x < 0$
  \[
  \opd{K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} < 0
  \]
  So by the 1st case of remark \ref{remark:I} we conclude
  \[
  \pd{\mathcal U(F, \phi)}{K}(\alpha, K, \hat\phi) < 0  
  \]
\end{proof}
By numerically integration and optimization with respect to $\phi$,
the value of $\hat\phi$ can be obtained for given $u(\cdot)$ and given
values of $K, K', \alpha, \beta$. Figures \ref{fig:phi_hat_pareto5e-1}
and \ref{fig:phi_hat_pareto4} show the values of $\hat\phi$ for
$u(C) = -\frac{C^{-\xi}}{\xi}$ with $\xi = 1/2, 4$ respectively.
$\beta=\alpha$ and $K'=K$ in both figures.
\begin{figure}
  \begin{subfigure}[b]{0.5\linewidth}
    \includegraphics[width=\textwidth]{phi_hat_pareto5e-1.pdf}
    \caption{$\hat\phi$ when $\xi = 1/2$}
    \label{fig:phi_hat_pareto5e-1}
  \end{subfigure}
  \begin{subfigure}[b]{0.5\linewidth}
    \includegraphics[width=\textwidth]{phi_hat_pareto4.pdf}
    \caption{$\hat\phi$ when $\xi = 4$}
    \label{fig:phi_hat_pareto4}
  \end{subfigure}
  \caption{$\hat\phi$, the optimal equity allocation when the utility
    function is $u(C) = -{C^{-\xi} \over \xi}$ for $\xi = 1/2, 4$.
  }
\end{figure}

@@

\subsection{Student's t-distributed equity return}
It is a common practice to use Student's t-distribution to model the
stationary distribution of equity returns. So it is of interest to
find out what implications this distribution has when it is combined
with the PDA preference. Formally we assume
\[
f(x; \nu) = c(\nu) \left(
  1 + {x^2 \over \nu}
\right)^{-(\nu + 1)/2}
\]
where $\nu > 1$ and
\[
c(\nu) = {
  \Gamma({\nu + 1 \over 2})
  \over
  \Gamma(\nu/2) \sqrt{\nu \pi}
}
\]
We can write $\mathcal U(F, \phi)$ as
\begin{eqnarray}
  && \mathcal U(F, \phi) \nonumber \\
  &=&
  \int_{0}^{\infty}
  \left[
    u(C(x, \phi)) + (1 + b)u(C(-x, \phi))
  \right]
  f(x, \nu) dx \nonumber \\
  &&
  + b \int_{0}^{q}
  u(C(x, \phi))
  f(x, \nu) dx - b u(C(q, \phi)) F(q, \nu)
  \label{eq:t1}
\end{eqnarray}
where $C(\cdot)$ is defined in \eqref{eq:xxie1}.

\begin{lemma}
  \label{lemma:II}
  There exists $x_0 > 0$ such that $\pd{f}{\nu}(x_0, \nu) = 0$ and
  $\forall x \in (0, x_0), \pd{f}{\nu}(x, \nu) > 0$ and
  $\forall x \in (x_0, \infty), \pd{f}{\nu}(x, \nu) < 0$.
\end{lemma}

\subsubsection{log-utility function}
We first consider the case where the utility function is simply
$u(\cdot) = \ln(\cdot)$. This corresponds to the limiting case of
\eqref{eq:power_utility} as $\gamma \to 0$.

First notice that when $b = 0$, $\mathcal U(F, \phi)$ reduces to
$\E u(C(X, \phi))$. Only the first integral of \eqref{eq:t1} remains.
Its integrand becomes $\ln[C(x, \phi) C(-x, \phi)]$.
Now observe $\ln(C(x, \phi)C(-x, \phi))$ is an increasing function of
$x$:
\begin{eqnarray*}
  \pd{C(x, \phi) C(-x, \phi)}{x}
  &=&
  \phi e^r (1 - \phi) (e^x - e^{-x}) > 0
\end{eqnarray*}
Thus when $b = 0$, by 1st case of remark \ref{remark:I} and lemma
\ref{lemma:II},
$\pd{\mathcal U(F, \phi))}{\nu} < 0$ for all $\phi$. Hence all
investors guided by this utility function would be seeking the
smallest $\nu$, i.e. the heaviest tail in the market.

@@

\subsubsection{power-utility function}
In this section we consider the case when the utility function
$u(\cdot)$ takes the form
\[
u(C) = -{1 \over \xi} C^{-\xi}
\]
Another major difference caused by a non-zero value of $b$ is seen in
the value of $\hat\phi$. When $b = 0$, $\hat\phi$ increases
continuously with $\nu$ as shown in figure \ref{fig:phi_hat_t5e-1};
when $b > 0$, $\hat\phi$ instead increases by jumping up at a sequence
of values of $\nu$. This is shown in figure \ref{fig:phi_hat_b_t5e-1}.
\begin{figure}[htb!]
  \begin{subfigure}[b]{0.5\linewidth}
    \includegraphics[width=\textwidth]{phi_hat_t5e-1.pdf}
    \caption{$\hat\phi$ when $b = 0$}
    \label{fig:phi_hat_t5e-1}
  \end{subfigure}
  \begin{subfigure}[b]{0.5\linewidth}
    \includegraphics[width=\textwidth]{phi_hat_b_t5e-1.pdf}
    \caption{$\hat\phi$ when $b = 0.01$}
    \label{fig:phi_hat_b_t5e-1}
  \end{subfigure}
  \caption{$\hat\phi$, the optimal equity allocation when the utility
    function is $u(C) = -{2 \over \sqrt{C}}$
  }
\end{figure}

@@

\section{Data analysis}
\subsection{Hill Estimator}
\label{sec:Hill}
There have been several estimators for the tail index proposed in the
literature, e.g. Hill (1975) \cite{hill1975simple}, Pikands (1975)
\cite{pickands1975statistical}, Dekkers and Einmahl and De Haan (1989)
\cite{dekkers1989moment}. See also Embrechts and Kl\"uppelberg and
Mikosch (1997)\cite{Embrechts1997}. The most popular of these is
arguably Hill (1975) \cite{hill1975simple}:
\[
\hat \alpha = \left[
  {1 \over k} \sum_{i=1}^k \ln {x_{(i)} \over x_{(k+1)}}
  \right]^{-1}
\]
where $x_{(i)}$ is the $i$-th upper order statistic of a sample
$x_1, x_2, ..., x_n$. It has been shown that the Hill estimator is
applicable to 
\begin{itemize}
\item iid random variables (Mason (1982) \cite{mason1982laws})
\item a weakly dependent sequence (Rootz{\'e}n, Leadbetter,
  and de Haan \cite{rootzen1992tail})
\item a linear process (Resnick and St{\u{a}}ric{\u{a}} (1995)
  \cite{resnick1995consistency}).
\end{itemize}
In these cases it is shown that, if $k \to \infty$ and $k/n \to 0$
as $n \to \infty$, the Hill estimator is weakly consistent, i.e.
\[
\sqrt k (\hat \alpha - \alpha) \overset{d}{\to} N(0, \alpha^2)
\]

Figure \ref{fig:Energy_lower},
\ref{fig:Consumer_Staples_lower},
and \ref{fig:Information_Technology_lower}
show the Hill estimates of the
lower tail indices of the ``energy'', ``consumer staples'' and ``information
technology'' sectors of the S\&P 500 index, respectively.
\begin{figure}[htb!]
  \centering
  \begin{subfigure}[b]{\linewidth}
    \includegraphics[width=\textwidth, trim={0, 0.8cm, 0, 2cm}, clip]
                    {Energy_lower.pdf}
    \caption{``Energy'' sector of S\&P 500}
    \label{fig:Energy_lower}
  \end{subfigure}
  \begin{subfigure}[b]{\linewidth}
    \includegraphics[width=\textwidth, trim={0, 0.8cm, 0, 2cm}, clip]
                    {Consumer_Staples_lower.pdf}
    \caption{``Consumer Staples'' sector of S\&P 500}
    \label{fig:Consumer_Staples_lower}
  \end{subfigure}
  \begin{subfigure}[b]{\linewidth}
    \includegraphics[width=\textwidth, trim={0, 0.8cm, 0, 2cm}, clip]
                    {Information_Technology_lower.pdf}
    \caption{``Information Technology'' sector of S\&P 500}
    \label{fig:Information_Technology_lower}
  \end{subfigure}
  \caption{\small Hill estimates of lower tail indices of
    daily return series in sectors of Standard \& Poor
    500 index. Each circle coresponds to a Hill estimate; the grey
    triangles above and below it mark the 97.5\% and 2.5\% quantiles
    of its approximate normal distribution.
    The low and high red lines mark the median of the 2.5\% quantiles
    and median of the 97.5\% quantiles, respectively.
    The data are from {\it Yahoo Finance} and the labels on
    the horizontal axis are Yahoo symbols of the stocks. The data span
    from 2010-01-01 to 2015-01-01 and comprise $n=1304$
    observations. $k=50$ lower order statistics are used
    for computing $\alpha_n$. 
  }
\end{figure}

\subsection{Hybrid fitting of the shifted Pareto distribution}
\label{sec:hybrid_estimation}
We adopt a hybrid procedure to estimate the parameters of the
distribution function assumed in \eqref{eq:X_distr}: First we
obtain a Hill estimate of the lower-tail indices of an
equity return and fix $\alpha$ in \eqref{eq:X_distr}
to its Hill estimate. Then we estimate $K$ by maximizing
the likelihood function with fixed $\alpha$. Obviously we take only
negative observations and hence condition on $X < 0$.

@@

\subsection{Pickand's Estimator}
Pickands (1975) \cite{pickands1975statistical} proposed a different
approach to estimate the tail index than that of Hill. Assume
$\{x_i\}_{i=1}^n$ are samples from the distribution of $X$ and let $U(t)$
denote the quantile of $1 - 1/t$ of this distribution, i.e.
\[
P(X > U(t)) = {1 \over t}
\]
The key idea of Pickands' estimator is to observe
\[
\lim_{t \to \infty} {
  U(c(t) t) - U(t)
  \over
  U(t) - U(t/c(t))
} = 2^{1/\alpha}
\]
for any function $c(t)$ satisfying $c(t) \to 2$ as $t \to \infty$.
Pickands formulated the estimation problem in terms of the extreme
value index $\xi$, which is the reciprocal of the tail index $\alpha$
when the distribution of $X$ is regularly varying (cf. Embrechtsm,
Kl\"uppelberg and Mikosch \cite{Embrechts1997}).
